### 2025-05-14 sec/introduction.tex
[update] changes listing and figures

\begin{itemize}
    \item Making sense of data-driven claims is hard, even if the evidence base (code/data) is open
    \item We see this in peer review, misinformation, retracted papers, …
\end{itemize}

@@

\begin{table}[!ht]
    \centering
    \footnotesize
    \renewcommand{\arraystretch}{1.5}
    \begin{tabular}{>{\raggedright\arraybackslash}p{2cm} >{\raggedright\arraybackslash}p{5cm} >{\raggedright\arraybackslash}p{6cm}}
        \toprule
        \textbf{Type}                & \textbf{Example} & \textbf{Generated Expression} \\
        \midrule
        \multicolumn{3}{>{\raggedright\arraybackslash}c}{\textbf{Quantitative expressions.}} \\
        \midrule
        Numerical value
        & BiLSTM gives significantly better accuracies compared to uni-directional LSTM2, with the training time per epoch growing from \hl{67} seconds to 106 seconds. &
        \begin{lstlisting}[language=Fluid,numbers=none]
(findWithKey' "model" "LSTM" tableData).time\_s
        \end{lstlisting} \\
        Percentage &
        The Energy Sector accounts for total methane emissions of \hl{52.80\%} in 2030. &
        \begin{lstlisting}[language=Fluid,numbers=none]
(record.emissions / sum(map (fun x -> x.emissions) (getByYear year tableData))) * 100
        \end{lstlisting}  \\
        Rounded or normalised number & ~                & ~                             \\
        \multicolumn{3}{>{\raggedright\arraybackslash}c}{\textbf{Aggregation.}} \\
        \midrule
        Average
        & The average methane emissions for the year 2030 is \hl{13.51} &
        \begin{lstlisting}[language=Fluid,numbers=none]
(sumEmissions year tableData / length records)
        \end{lstlisting} \\
        Min                          & ~                & ~                             \\
        Max                          & ~                & ~                             \\\
        Ranks &
        On the other hand, a 3-layer stacked CNN gives an accuracy of 81.46\%, which is also the \hl{lowest} compared with BiLSTM, hierarchical attention and S-LSTM  &
        \begin{lstlisting}[language=Fluid,numbers=none]
let pos = findIndex "model" "CNN" (insertionSort cmpTime tableData) in rankLabel "lowest" pos
        \end{lstlisting} \\
        Total &
        The total methane emissions for the year 2030 is \hl{37.74} for Agriculture &
        \begin{lstlisting}[language=Fluid,numbers=none]
sumEmissions year tableData
        \end{lstlisting} \\
        *Count                       & ~                & ~                             \\
        \multicolumn{3}{>{\raggedright\arraybackslash}c}{\textbf{Trends \& Adjectives.}} \\
        \midrule
        Comparisons
        & BiLSTM gives significantly better accuracies compared to uni-directional LSTM2, with the training time per epoch \hl{growing from} 67 seconds to 106 seconds. &
        \begin{lstlisting}[language=Fluid,numbers=none]
trendWord (findWithKey' "model" "BiLSTM" tableData).time\_s (findWithKey' "model" "LSTM" tableData).time\_s "growing from" "shrinking to" "equal to"
        \end{lstlisting} \\
        *Graded adjective            & ~                & ~                             \\
        *Reference to visual element                            & ~                & ~                             \\
        \bottomrule
    \end{tabular}
    \caption{Example expressions generated by the Authoring Assistant, classified by type. In green, the expression is already tested.}
    \label{tab:fluid_examples}
    \renewcommand{\arraystretch}{1.0}
\end{table}

>>>>

\begin{itemize}
    \item Interactive visualization of data
    \item Making the text transparent, with the possibility to highlight the data related to a specific sentence.
    \item Making sense of data-driven claims is hard, even if the evidence base (code/data) is open
    \item We see this in peer review, misinformation, retracted papers, …
\end{itemize}

@@

\begin{table}[!ht]
    \centering
    \footnotesize
    \renewcommand{\arraystretch}{1.5}
    \begin{tabular}{>{\raggedright\arraybackslash}p{2cm} >{\raggedright\arraybackslash}p{5cm} >{\raggedright\arraybackslash}p{6cm}}
        \toprule
        \textbf{Type}                & \textbf{Example} & \textbf{Generated Expression} \\
        \midrule
        \rowcolor{gray!20}
        \multicolumn{3}{>{\raggedright\arraybackslash}c}{\textbf{Quantitative expressions.}} \\
        \midrule
        Numerical value
        & BiLSTM gives significantly better accuracies compared to uni-directional LSTM2, with the training time per epoch growing from \hl{67} seconds to 106 seconds. &
        \begin{lstlisting}[language=Fluid,numbers=none]
(findWithKey' "model" "LSTM" tableData).time_s
        \end{lstlisting} \\
        Percentage &
        The Energy Sector accounts for total methane emissions of \hl{52.80\%} in 2030.
        & \begin{lstlisting}[language=Fluid,numbers=none]
(record.emissions /
 sum (map (fun x -> x.emissions)
          (getByYear year tableData))) * 100

        \end{lstlisting}  \\
        Rounded or normalised number & ~                & ~                             \\
        \multicolumn{3}{>{\raggedright\arraybackslash}c}{\textbf{Aggregation.}} \\
        \midrule
        Average
        & The average methane emissions for the year 2030 is \hl{13.51} &
        \begin{lstlisting}[language=Fluid,numbers=none]
(sumEmissions year tableData / length records)
        \end{lstlisting} \\
        Min                          & ~                & ~                             \\
        Max                          & ~                & ~                             \\
        Ranks &
        On the other hand, a 3-layer stacked CNN gives an accuracy of 81.46\%, which is also the \hl{lowest} compared with BiLSTM, hierarchical attention and S-LSTM  &
        \begin{lstlisting}[language=Fluid,numbers=none]
let pos =
  findIndex
    "model"
    "CNN"
    (insertionSort cmpTime tableData)
in rankLabel "lowest" pos
        \end{lstlisting} \\
        Total &
        The total methane emissions for the year 2030 is \hl{37.74} for Agriculture &
        \begin{lstlisting}[language=Fluid,numbers=none]
sumEmissions year tableData
        \end{lstlisting} \\
        *Count                       & ~                & ~                             \\
        \multicolumn{3}{>{\raggedright\arraybackslash}c}{\textbf{Trends \& Adjectives.}} \\
        \midrule
        Comparisons
        & BiLSTM gives significantly better accuracies compared to uni-directional LSTM2, with the training time per epoch \hl{growing from} 67 seconds to 106 seconds. &
        \begin{lstlisting}[language=Fluid,numbers=none]
trendWord
 (findWithKey' "model" "BiLSTM" tableData).time_s
 (findWithKey' "model" "LSTM" tableData).time_s
 growShrink
        \end{lstlisting} \\
        *Graded adjective            & ~                & ~                             \\
        *Reference to visual element                            & ~                & ~                             \\
        \bottomrule
    \end{tabular}
    \caption{Example expressions generated by the Authoring Assistant, classified by type. In green, the expression is already tested.}
    \label{tab:fluid_examples}
    \renewcommand{\arraystretch}{1.0}
\end{table}
